Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-11-13 awipev-CO2_PAR_sal.Rmd

########### Binding sal_fb + sal_insitu if we get gaps in sal_insitu = call this new column = sal_mix ########### 
d_all <- d_all %>%
  dplyr::mutate(sal_mix = ifelse(!is.na(sal_fb), sal_fb, sal_insitu_ctd_9m))
```
## Plot

```{r PAR / SAL Dygraph, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
#xts + dygraph
sal_xts <- dplyr::select(d_all, datetime,sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_9m, par_insitu_profile_1m, par_insitu_profile_3m, par_insitu_profile_5m, par_insitu_profile_7m, par_insitu_profile_9m)%>%
   dplyr::filter(!is.na(datetime))

sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
dygraph(sal_xts, group = "awipev", main="Salinity (in FerryBox)", ylab="Salinity") %>%
   dySeries("sal_insitu_ctd_1m", color = "blue", strokeWidth = 0, label = "SAL 1 m") %>%
   dySeries("sal_insitu_ctd_3m", color = "blue", strokeWidth = 0, label = "SAL 3 m") %>%
   dySeries("sal_insitu_ctd_5m", color = "blue", strokeWidth = 0, label = "SAL 5 m") %>%
   dySeries("sal_insitu_ctd_7m", color = "blue", strokeWidth = 0, label = "SAL 7 m") %>%
   dySeries("sal_insitu_ctd_9m", color = "blue", strokeWidth = 0, label = "SAL 9 m") %>%
   dySeries("par_insitu_profile_1m", color = "red", strokeWidth = 0, label = "PAR 1 m",axis = "y2") %>%
   dySeries("par_insitu_profile_3m", color = "red", strokeWidth = 0, label = "PAR 3 m",axis = "y2") %>%
   dySeries("par_insitu_profile_5m", color = "red", strokeWidth = 0, label = "PAR 5 m",axis = "y2") %>%
   dySeries("par_insitu_profile_7m", color = "red", strokeWidth = 0, label = "PAR 7 m",axis = "y2") %>%
   dySeries("par_insitu_profile_9m", color = "red", strokeWidth = 0, label = "PAR 9 m",axis = "y2") %>%

dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
      dyOptions( drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
    dyLegend(show = "follow")   %>%
   dyAxis("y2",valueRange = c(0, 1350), label = "PAR") %>%
      dyRangeSelector(height = 30, dateWindow= NULL)
```

## Relationships

@@

>>>>

########### Binding sal_fb + sal_insitu if we get gaps in sal_insitu = call this new column = sal_mix ########### 
d_all <- d_all %>%
  dplyr::mutate(sal_mix = ifelse(!is.na(sal_fb), sal_fb, sal_insitu_ctd_9m))
```

```{r data filter, echo=FALSE, fig.height=4, fig.width=10, message=FALSE, warning=FALSE}
#select mummer months
june2018 <- d_all %>%
  dplyr::select(datetime, par_insitu_profile_1m, par_insitu_profile_3m, par_insitu_profile_5m, par_insitu_profile_7m, par_insitu_profile_9m, par_air, turb_fb, sal_fb, sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_9m) %>% 
  dplyr::filter(datetime >= "2018-06-01 00:00:00" & datetime <= "2018-06-30 23:59:59")%>% 
  dplyr::mutate(day = day(datetime))

july2018 <- d_all %>%
  dplyr::select(datetime, par_insitu_profile_1m, par_insitu_profile_3m, par_insitu_profile_5m, par_insitu_profile_7m, par_insitu_profile_9m, par_air, turb_fb, sal_fb, sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_9m) %>% 
  dplyr::filter(datetime >= "2018-07-01 00:00:00" & datetime <= "2018-07-31 23:59:59")%>% 
  dplyr::mutate(day = day(datetime))

august2018 <- d_all %>%
  dplyr::select(datetime, par_insitu_profile_1m, par_insitu_profile_3m, par_insitu_profile_5m, par_insitu_profile_7m, par_insitu_profile_9m, par_air, turb_fb, sal_fb, sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_9m) %>% 
  dplyr::filter(datetime >= "2018-08-01 00:00:00" & datetime <= "2018-08-31 23:59:59") %>% 
  dplyr::mutate(day = day(datetime))

# summarise the max PAR/sal by day
sumjune2018 <- june2018 %>% 
  dplyr::group_by(day) %>% 
  dplyr:: summarise(maxPAR1m = max(par_insitu_profile_1m, na.rm=TRUE),
                  maxPAR3m = max(par_insitu_profile_3m, na.rm=TRUE),
                  maxPAR5m = max(par_insitu_profile_5m, na.rm=TRUE),
                  maxPAR7m = max(par_insitu_profile_7m, na.rm=TRUE),
                  maxPAR9m = max(par_insitu_profile_9m, na.rm=TRUE),
                  maxSAL1m = max(sal_insitu_ctd_1m, na.rm=TRUE),
                  maxSAL3m = max(sal_insitu_ctd_3m, na.rm=TRUE),
                  maxSAL5m = max(sal_insitu_ctd_5m, na.rm=TRUE),
                  maxSAL7m = max(sal_insitu_ctd_7m, na.rm=TRUE),
                  maxSAL9m = max(sal_insitu_ctd_9m, na.rm=TRUE),
                  maxPARair = max(par_air, na.rm=TRUE),
                  nb =n())

sumjuly2018 <- july2018 %>% 
  dplyr::group_by(day) %>% 
  dplyr:: summarise(maxPAR1m = max(par_insitu_profile_1m, na.rm=TRUE),
                  maxPAR3m = max(par_insitu_profile_3m, na.rm=TRUE),
                  maxPAR5m = max(par_insitu_profile_5m, na.rm=TRUE),
                  maxPAR7m = max(par_insitu_profile_7m, na.rm=TRUE),
                  maxPAR9m = max(par_insitu_profile_9m, na.rm=TRUE),
                  maxSAL1m = max(sal_insitu_ctd_1m, na.rm=TRUE),
                  maxSAL3m = max(sal_insitu_ctd_3m, na.rm=TRUE),
                  maxSAL5m = max(sal_insitu_ctd_5m, na.rm=TRUE),
                  maxSAL7m = max(sal_insitu_ctd_7m, na.rm=TRUE),
                  maxSAL9m = max(sal_insitu_ctd_9m, na.rm=TRUE),
                  maxPARair = max(par_air, na.rm=TRUE),
                  nb =n())

sumaugust2018 <- august2018 %>% 
  dplyr::group_by(day) %>% 
  dplyr:: summarise(maxPAR1m = max(par_insitu_profile_1m, na.rm=TRUE),
                  maxPAR3m = max(par_insitu_profile_3m, na.rm=TRUE),
                  maxPAR5m = max(par_insitu_profile_5m, na.rm=TRUE),
                  maxPAR7m = max(par_insitu_profile_7m, na.rm=TRUE),
                  maxPAR9m = max(par_insitu_profile_9m, na.rm=TRUE),
                  maxSAL1m = max(sal_insitu_ctd_1m, na.rm=TRUE),
                  maxSAL3m = max(sal_insitu_ctd_3m, na.rm=TRUE),
                  maxSAL5m = max(sal_insitu_ctd_5m, na.rm=TRUE),
                  maxSAL7m = max(sal_insitu_ctd_7m, na.rm=TRUE),
                  maxSAL9m = max(sal_insitu_ctd_9m, na.rm=TRUE),
                  maxPARair = max(par_air, na.rm=TRUE),
                  nb =n())
# tables
kable(sumjune2018, caption ="June 2018")
kable(sumjuly2018, caption ="July 2018")
kable(sumaugust2018, caption ="August 2018")
```
### Plot

```{r PAR / SAL Dygraph, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
#xts + dygraph
sal_xts <- dplyr::select(d_all, datetime,sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_9m, par_insitu_profile_1m, par_insitu_profile_3m, par_insitu_profile_5m, par_insitu_profile_7m, par_insitu_profile_9m, par_air)%>%
   dplyr::filter(!is.na(datetime))

sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
dygraph(sal_xts, group = "awipev", main="Salinity and PAR (in field)", ylab="") %>%
   dySeries("sal_insitu_ctd_1m", color = "blue", strokeWidth = 0, label = "SAL 1 m") %>%
   dySeries("sal_insitu_ctd_3m", color = "blue", strokeWidth = 0, label = "SAL 3 m") %>%
   dySeries("sal_insitu_ctd_5m", color = "blue", strokeWidth = 0, label = "SAL 5 m") %>%
   dySeries("sal_insitu_ctd_7m", color = "blue", strokeWidth = 0, label = "SAL 7 m") %>%
   dySeries("sal_insitu_ctd_9m", color = "blue", strokeWidth = 0, label = "SAL 9 m") %>%
   dySeries("par_insitu_profile_1m", color = "red", strokeWidth = 0, label = "PAR 1 m",axis = "y2") %>%
   dySeries("par_insitu_profile_3m", color = "red", strokeWidth = 0, label = "PAR 3 m",axis = "y2") %>%
   dySeries("par_insitu_profile_5m", color = "red", strokeWidth = 0, label = "PAR 5 m",axis = "y2") %>%
   dySeries("par_insitu_profile_7m", color = "red", strokeWidth = 0, label = "PAR 7 m",axis = "y2") %>%
   dySeries("par_insitu_profile_9m", color = "red", strokeWidth = 0, label = "PAR 9 m",axis = "y2") %>%
     dySeries("par_air", color = "orange", strokeWidth = 0, label = "PAR AIR",axis = "y2") %>%
dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
      dyOptions( drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
    dyLegend(show = "follow")   %>%
   dyAxis("y2",valueRange = c(0, 1350), label = "PAR") %>%
      dyRangeSelector(height = 30, dateWindow= NULL)

#plot 2
#Delete the NA line with datetime
fb_xts <- dplyr::select(d_all, datetime,sal_fb, turb_fb)
fb_xts <- fb_xts[-which(is.na(fb_xts$datetime)),]
fb_xts <- as.xts(fb_xts, order.by = fb_xts$datetime)
dygraph(fb_xts, group = "awipev", main="Salinity and Turbidity (in FerryBox)", ylab="") %>%
   dySeries("sal_fb", color = "blue", strokeWidth = 0, label = "SAL FB") %>%
   dySeries("turb_fb", color = "brown", strokeWidth = 0, pointSize = 4,label = "Turb FB",axis = "y2") %>%
dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
      dyOptions( drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
    dyLegend(show = "follow")   %>%
  dyAxis("y2",valueRange = c(0, 1000), label = "PAR") %>%
      dyRangeSelector(height = 30, dateWindow= NULL)
```

## Relationships by depths (first test)

@@

## Relationships by summer months (second test)

```{r PAR / SAL relationship summer months, echo=FALSE, fig.asp=0.5, out.width = "100%", message=FALSE, warning=FALSE}
#june
fit <- lm(data = sumjune2018, maxPAR7m ~ maxSAL7m)
p_june <- ggplot(sumjune2018,aes(x=maxSAL7m, y= maxPAR7m, label = day))+
  geom_text( aes(color=factor(day))) +
  scale_color_discrete(guide="none")+
    labs(x="Salinity June 7 m", y="PAR June 7 m", color = "Days")  +
    stat_smooth(method = "lm", col = "black") +
    labs(title = paste("", "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                       ";\nIntercept =",signif(fit$coef[[1]],5 ),
                       ";\nSlope =",signif(fit$coef[[2]], 5),
                       ";\nP =", signif(summary(fit)$coef[2,4], 5),
                       ";\nRMSE =", signif(sqrt(mean(fit$residuals^2)), 5))) +
  ylim(0,1500) +
  theme_bw() + theme(aspect.ratio=1,
        axis.text=element_text(size=7),
        axis.title.y= element_text(size =7),
        axis.title.x= element_text(size =7),
        plot.margin = unit(c(0.5,1,1,1), "cm"),
        plot.title = element_text(size=7, hjust=0.05,margin = margin(l = 10, b = -70)))
#july
fit <- lm(data = sumjuly2018, maxPAR7m ~ maxSAL7m)
p_july <- ggplot(sumjuly2018,aes(x=maxSAL7m, y= maxPAR7m, label = day))+
  geom_text( aes(color=factor(day))) +
  scale_color_discrete(guide="none")+
    labs(x="Salinity July 7 m", y="PAR July 7 m", color = "Days")  +
    stat_smooth(method = "lm", col = "black") +
    labs(title = paste("", "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                       ";\nIntercept =",signif(fit$coef[[1]],5 ),
                       ";\nSlope =",signif(fit$coef[[2]], 5),
                       ";\nP =", signif(summary(fit)$coef[2,4], 5),
                       ";\nRMSE =", signif(sqrt(mean(fit$residuals^2)), 5))) +
  ylim(0,1500) +
  theme_bw() + theme(aspect.ratio=1,
        axis.text=element_text(size=7),
        axis.title.y= element_text(size =7),
        axis.title.x= element_text(size =7),
        plot.margin = unit(c(0.5,1,1,1), "cm"),
        plot.title = element_text(size=7, hjust=0.05,margin = margin(l = 10, b = -70)))

#august
fit <- lm(data = sumaugust2018, maxPAR7m ~ maxSAL7m)
p_august <- ggplot(sumaugust2018,aes(x=maxSAL7m, y= maxPAR7m, label = day))+
  geom_text( aes(color=factor(day))) +
  scale_color_discrete(guide="none")+
    labs(x="Salinity August 7 m", y="PAR August 7 m", color = "Days")  +
    stat_smooth(method = "lm", col = "black") +
    labs(main ="August 2018", title = paste("", "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                       ";\nIntercept =",signif(fit$coef[[1]],5 ),
                       ";\nSlope =",signif(fit$coef[[2]], 5),
                       ";\nP =", signif(summary(fit)$coef[2,4], 5),
                       ";\nRMSE =", signif(sqrt(mean(fit$residuals^2)), 5))) +
  ylim(0,1500) +
  theme_bw() + theme(aspect.ratio=1,
        axis.text=element_text(size=7),
        axis.title.y= element_text(size =7),
        axis.title.x= element_text(size =7),
        plot.margin = unit(c(0.5,1,1,1), "cm"),
        plot.title = element_text(size=7, hjust=0.05,margin = margin(l = 10, b = -70)))

print(p_june)
print(p_july)
print(p_august)
```
